\begin{thebibliography}{8}
	\bibitem{kopp2020smt2020}
	Kopp, D., Hassoun, M., Kalir, A., Mönch, L.: SMT2020—a semiconductor manufacturing testbed. IEEE Transactions on Semiconductor Manufacturing 33(4):522–531 (2020)
	
	\bibitem{Hopp2011}
	Hopp, W. J., Spearman, M. L.: Factory physics. Waveland Press. (2011)
	
	\bibitem{Uzsoy1992}
	Uzsoy, R., Lee, C. Y., Martin-Vega, L. A.: A review of production planning and scheduling models in the semiconductor industry part I: system characteristics, performance evaluation and production planning. IIE transactions, 24(4), 47-60 (1992)
	
	\bibitem{schumann2022scheduling}
	Pinedo, M. L.: Scheduling: theory, algorithms, and systems. 6th edn. Springer (2022) 
	
	\bibitem{May2006}
	May, G. S., Spanos, C. J.: Fundamentals of semiconductor manufacturing and process control. John Wiley \& Sons. (2006)
	
	\bibitem{Mönch2011}
	Mönch, L., Fowler, J. W., Dauzère-Pérès, S., Mason, S. J., Rose, O.: A survey of problems, solution techniques, and future challenges in scheduling semiconductor manufacturing operations. Journal of scheduling, 14, 583-599. (2011)
	
	\bibitem{Ali2024}
	Ali, R., Qaiser, S., El-Kholany, M. M., Eftekhari, P., Gebser, M., Leitner, S., Friedrich, G. A Greedy Search Based Ant Colony Optimization Algorithm for Large-Scale Semiconductor Production. In Proceedings of the 14th International Conference on Simulation and Modeling Methodologies, Technologies and Applications (SIMULTECH 2024), pages 138-149. (2024)
	
	\bibitem{Dorigo2019}
	Dorigo, M., Stützle, T.: Ant colony optimization: overview and recent advances. In Handbook of Metaheuristics, pages 311–351. Springer (2019)
	
	\bibitem{Papadimitriou}
	Papadimitriou, C. H., Steiglitz, K.: Combinatorial Optimization: Algorithms and Complexity. Prentice-Hall. (1982)
	
	\bibitem{Perron2023}
	Perron, L., Didier, F., Gay, S.: The CP-SATLP
	solver (invited talk). In Proceedings of the 29th
	International Conference on Principles and Practice
	of Constraint Programming, pages 3:1–3:2. Leibniz
	International Proceedings in Informatics, (2023)
	
	\bibitem{Kovács2022}
	Kovács, B., Tassel, P., Ali, R., El-Kholany, M., Gebser, M., Seidel, G.: A customizable simulator for artificial intelligence research to schedule semiconductor fabs. In 2022 33rd Annual SEMI Advanced Semiconductor Manufacturing Conference (ASMC) (pp. 1-6). IEEE, (2022, May)
	
	\bibitem{waschneck2018deep}
	Waschneck, B., Reichstaller, A., Belzner, L., Altenmüller, T., Bauernhansl, T., Knapp, A., Kyek, A.: Deep reinforcement learning for semiconductor production scheduling. In 2018 29th annual SEMI advanced semiconductor manufacturing conference (ASMC) pp. 301-306. IEEE, (2018, April)
	
	\bibitem{leachman1996benchmarking}
	Leachman, R. C., Hodges, D. A.: Benchmarking semiconductor manufacturing. IEEE transactions on semiconductor manufacturing 9(2), 158-169 (1996)
	
	\bibitem{McKay2003}
	McKay, K. N., Wiers, V. C.: Planning, scheduling and dispatching tasks in production control. Cognition, Technology \& Work, 5, 82-93 (2003)
	
	\bibitem{chan2024situation}
	Chan, C. W.: Situation aware dispatching system for semiconductor manufacturing, (2024)
	
	\bibitem{may2006}
	May, G. S., Spanos, C. J.: Fundamentals of semiconductor manufacturing and process control. John Wiley \& Sons, (2006)
	
	\bibitem{Monch2012}
	Mönch, L., Fowler, J. W., Mason, S. J.: Production planning and control for semiconductor wafer fabrication facilities: modeling, analysis, and systems (Vol. 52). Springer Science \& Business Media, (2012) 

    \bibitem{el2023}
	El-Kholany, M., Ali, R., Gebser, M.: Hybrid ASP-based multi-objective scheduling of semiconductor manufacturing processes (Extended version). arXiv preprint arXiv:2307.14799,  (2023)
	
	\bibitem{dauzere2024flexible}
	Shen, L., Dauzère-Pérès, S., Neufeld, J. S.: Solving the flexible job shop scheduling problem with sequence-dependent setup times. European journal of operational research, 265(2), 503-516, (2018)
	
	\bibitem{lei2022multi}
	Lei, K., Guo, P., Zhao, W., Wang, Y., Qian, L., Meng, X., Tang, L.: A multi-action deep reinforcement learning framework for flexible Job-shop scheduling problem. Expert Systems with Applications, 205, 117796, (2022)
	
	\bibitem{nayar2021ant}
	Nayar, N., Gautam, S., Singh, P., Mehta, G.: Ant colony optimization: A review of literature and application in feature selection. Inventive Computation and Information Technologies: Proceedings of ICICIT 2020, 285-297, (2021)
	
	\bibitem{zhou2022parameter}
	Zhou, X., Ma, H., Gu, J., Chen, H., Deng, W.: Parameter adaptation-based ant colony optimization with dynamic hybrid mechanism. Engineering Applications of Artificial Intelligence, 114, 105139,  (2022)
	
	\bibitem{dorigo2019ant}
	Dorigo, M.,  Stützle, T.: Ant colony optimization: overview and recent advances (pp. 311-351). Springer International Publishing, (2019)
	
	\bibitem{stutzle1999aco}
	Stützle, T., Dorigo, M.: ACO algorithms for the traveling salesman problem. Evolutionary algorithms in engineering and computer science, 4, 163-183, (1999)
	
	\bibitem{rizzoli2007ant}
	Rizzoli, A. E., Montemanni, R., Lucibello, E., Gambardella, L. M.: Ant colony optimization for real-world vehicle routing problems: from theory to applications. Swarm Intelligence, 1, 135-151, (2007)
	
	\bibitem{luo2008ant}
	Luo, D. L., Wu, S. X., Li, M. Q., Yang, Z.: Ant colony optimization with local search applied to the flexible job shop scheduling problems. In 2008 International Conference on Communications, Circuits and Systems (pp. 1015-1020). IEEE, (2008)
	
	\bibitem{rugwiro2019task}
	Rugwiro, U., Gu, C., Ding, W.: Task scheduling and resource allocation based on ant-colony optimization and deep reinforcement learning. Journal of Internet Technology, 20(5), 1463-1475, (2019)
	
	\bibitem{khelifa2020holonic}
	Khelifa, B., Laouar, M. R.: A holonic intelligent decision support system for urban project planning by ant colony optimization algorithm. Applied Soft Computing, 96, 106621, (2020)
	
	\bibitem{wang2009hopnet}
	Wang, J., Osagie, E., Thulasiraman, P., Thulasiram, R. K.: HOPNET: A hybrid ant colony optimization routing algorithm for mobile ad hoc network. Ad Hoc Networks, 7(4), 690-705, (2009)
	
	
	\bibitem{turkyilmaz2020research}
	Türkyılmaz, A., Şenvar, Ö., Ünal, I., Bulkan, S.: A research survey: heuristic approaches for solving multi objective flexible job shop problems. Journal of Intelligent Manufacturing, 31(8), 1949-1983,  (2020)
	
	
	
	\bibitem{leung2010integrated}
	Leung, C. W., Wong, T. N., Mak, K. L., Fung, R. Y.: Integrated process planning and scheduling by an agent-based ant colony optimization. Computers \& Industrial Engineering, 59(1), 166-180,  (2010)
	
	\bibitem{li2010improved}
	Li, L., Keqi, W., Chunnan, Z.: An improved ant colony algorithm combined with particle swarm optimization algorithm for multi-objective flexible job shop scheduling problem. In 2010 International Conference on Machine Vision and Human-machine Interface (pp. 88-91). IEEE, (2010)
	
	\bibitem{xing2010knowledge}
	Xing, L. N., Chen, Y. W., Wang, P., Zhao, Q. S., Xiong, J.: A knowledge-based ant colony optimization for flexible job shop scheduling problems. Applied Soft Computing, 10(3), 888-896,  (2010)
	
	\bibitem{thammano2013hybrid}
	Thammano, A., Phu-ang, A.: A hybrid artificial bee colony algorithm with local search for flexible job-shop scheduling problem. Procedia computer science, 20, 96-101, (2013)
	
	\bibitem{arnaout2014two}
	Arnaout, J. P., Musa, R., Rabadi, G.: A two-stage Ant Colony optimization algorithm to minimize the makespan on unrelated parallel machines—part II: enhancements and experimentations. Journal of Intelligent Manufacturing, 25, 43-53, (2014)
	
	\bibitem{el2017dual}
	El Khoukhi, F., Boukachour, J., Alaoui, A. E. H.: The “Dual-Ants Colony”: A novel hybrid approach for the flexible job shop scheduling problem with preventive maintenance. Computers \& Industrial Engineering, 106, 236-255,  (2017)
	
	
	\bibitem{abdel2021hybrid}
	Abdel-Basset, M., Ding, W., El-Shahat, D.: A hybrid Harris Hawks optimization algorithm with simulated annealing for feature selection. Artificial Intelligence Review, 54(1), 593-637, (2021)
	
	\bibitem{fontes2023hybrid}
	Fontes, D. B., Homayouni, S. M., Gonçalves, J. F.: A hybrid particle swarm optimization and simulated annealing algorithm for the job shop scheduling problem with transport resources. European Journal of Operational Research, 306(3), 1140-1157, (2023)
	
	\bibitem{li2021hybrid}
	Li, Q., Ning, H., Gong, J., Li, X., Dai, B.: A hybrid greedy sine cosine algorithm with differential evolution for global optimization and cylindricity error evaluation. Applied Artificial Intelligence, 35(2), 171-191, (2021)
	
	\bibitem{mohd2023improved}
	Mohd Tumari, M. Z., Ahmad, M. A., Suid, M. H., Hao, M. R.: An improved marine predators algorithm-tuned fractional-order PID controller for automatic voltage regulator system. Fractal and Fractional, 7(7), 561, (2023)
	
	\bibitem{suid2023novel}
	Suid, M. H., Ahmad, M. A.: A novel hybrid of Nonlinear Sine Cosine Algorithm and Safe Experimentation Dynamics for model order reduction. Automatika: časopis za automatiku, mjerenje, elektroniku, računarstvo i komunikacije, 64(1), 34-50, (2023)
	
	\bibitem{kumar1993}
	Kumar, P. R.: Re-entrant lines. Queueing systems, 13(1), 87-110, (1993)
	
	\bibitem{baker1974}
	Baker, K. R.: Introduction to sequencing and scheduling. John Wiley and Sons google schola, 2, 560-562, (1974)
	
	\bibitem{blackstone1982}
	Blackstone, J. H., Phillips, D. T., Hogg, G. L.: A state-of-the-art survey of dispatching rules for manufacturing job shop operations. The International Journal of Production Research, 20(1), 27-45, (1982)
	
	\bibitem{pediga23a}
	Perron, L., Didier, F., Gay, S.: The CP-SAT-LP Solver (Invited Talk). In 29th International Conference on Principles and Practice of Constraint Programming (CP 2023). Schloss-Dagstuhl-Leibniz Zentrum für Informatik, (2023)
	
	\bibitem{kubec16a}
	Ku, W. Y., Beck, J. C.: Mixed integer programming models for job shop scheduling: A computational analysis. Computers \& Operations Research, 73, 165-173, (2016)
	
	\bibitem{fattahi2007mathematical}
	Fattahi, P., Saidi Mehrabad, M., Jolai, F.: Mathematical modeling and heuristic approaches to flexible job shop scheduling problems. Journal of intelligent manufacturing, 18, 331-342, (2007)
	
	\bibitem{brandimarte1993routing}
	Brandimarte, P.: Routing and scheduling in a flexible job shop by tabu search. Annals of Operations research, 41(3), 157-183, (1993)
	
	
	\bibitem{ref_article1}
	Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
	
	\bibitem{ref_lncs1}
	Author, F., Author, S.: Title of a proceedings paper. In: Editor,
	F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
	Springer, Heidelberg (2016). \doi{10.10007/1234567890}
	
	\bibitem{ref_book1}
	Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
	Location (1999)
	
	\bibitem{ref_proc1}
	Author, A.-B.: Contribution title. In: 9th International Proceedings
	on Proceedings, pp. 1--2. Publisher, Location (2010)
	
	\bibitem{ref_url1}
	LNCS Homepage, \url{http://www.springer.com/lncs}, last accessed 2023/10/25
\end{thebibliography}