%As the digital transformation deepens across various sectors, the demand for more powerful, energy-efficient, and smaller semiconductors continues to escalate. This surge in demand places immense pressure on semiconductor manufacturers to scale up production without compromising quality. Semiconductor production involves hundreds of sophisticated steps, each of which must be precisely controlled to ensure the functionality and yield of the final product \cite{kopp2020smt2020}. The complexity is exacerbated by the rapid pace of innovation in semiconductor design, which frequently shifts production parameters and process requirements.

Dispatching and scheduling strategies are critical in semiconductor manufacturing because they directly impact the production throughput and utilization of resources. Dispatching refers to the process of assigning production operations to specific machines in real-time, while scheduling involves pre-planning the sequencing and timing of operations to optimize certain key performance indicators, such as minimizing the completion time of scheduled operations or balancing the load across different machines~\cite{schumann2022scheduling}.

For smaller volumes at specific workcenters in a semiconductor fab, which can be modeled as flexible job shops, optimal solutions can be achieved using mathematical optimization \cite{waschneck2018deep}. However, in larger-scale and more dynamic environments, the high complexity and computational constraints limit the feasibility of applying mathematical optimization. Consequently, exact optimization is typically implemented at a local scale and isolated to individual workcenters. In complex scenarios, this localized approach to production scheduling cannot guarantee the global performance of a semiconductor fab.

Dispatching involves prioritizing operations and determining the machines to perform them. These decisions are based on the availability of resources and the urgency of jobs \cite{Hopp2011}. However, as production scenarios become complex, particularly in high-tech industries such as semiconductor manufacturing, the static nature of traditional dispatching rules often turns out to be insufficient. Static dispatching rules do not account for rapid changes in production conditions or intricate dependencies between different production processes.  
% Traditional dispatching solutions often fall short in such an environment, as they cannot adequately adapt to the dynamic and complex nature of semiconductor production.
This inadequacy can lead to sub-optimal dispatching decisions that compromise operational efficiency \cite{Uzsoy1992}.

The complexity of scheduling in large-scale semiconductor production % , a cornerstone of operational management,
is significantly influenced by the unpredictable nature of processing times and machine availabilities~\cite{May2006}. Variability in processing times can arise from differences in equipment conditions, material handling durations, or the unique characteristics of production lots, while frequent machine breakdowns can cause substantial disruptions, underscoring the need for strong and adaptable scheduling strategies \cite{leachman1996benchmarking}.
The complexity is further compounded by the need to accommodate a wide mix of product types, each with distinct processing needs and priorities, and to integrate new processes seamlessly into the production schedule without disrupting ongoing operations~\cite{Moench2011}.
Scheduling involves meticulously planning and organizing production operations to achieve optimal resource utilization and synchronized product flows across various manufacturing stages, which is crucial for minimizing the makespan of schedules and maintaining high throughput~\cite{schumann2022scheduling}. % The task is particularly daunting in semiconductor manufacturing due to the high variability in production processes, the sensitive nature of the materials, and stringent quality requirements \cite{May2006}. 
% Each semiconductor product may pass through hundreds of processing steps, requiring precise timing and coordination.

In this paper, we explore the capacities of scheduling for large-scale Semiconductor Manufacturing Scheduling Problems (SMSPs), representing the operations of semiconductor fabs. 
% Fabs are intricate production settings distinguished by their specialized job flows and advanced machinery.
Modern semiconductor fabs manage the processing of tens of thousands of operations daily across thousands of different machines~\cite{kopp2020smt2020}. These machines are grouped by functionality—such as diffusion, etching, or metrology—and each step in the manufacturing process can be assigned to any machine that offers the necessary capabilities. The scheduling challenge in semiconductor manufacturing thus involves assigning specific operations to appropriate machines and determining an optimal operation sequence on each machine. Additionally, schedules must be flexible and capable of rapid readjustments in response to machine failures or dynamic process deviations.

In our previous work \cite{Ali2024}, we proposed a Greedy Search-based Ant Colony Optimization (GSACO)
algorithm for (re-)scheduling semiconductor production operations. 
Our algorithm harnesses Ant Colony Optimization (ACO) \cite{Dorigo2019} for exploration, while
Greedy Search (GS) \cite{Papadimitriou} enables responses in short time. 
In this way, GSACO overcomes limitations of a state-of-the-art Constraint Programming (CP) approach \cite{Perron2023}
on large-scale SMSP instances. Our approach synergistically combines probabilistic operation sequencing with a greedy machine assignment strategy, targeting % up to five operations per lot with the primary 
the objective of minimizing makespan. Building on this foundational work, our paper extends the previous method by proposing an enhanced approach, GSACO-O, which is specifically designed to optimize the operational throughput of semiconductor fabs. This development marks a significant advancement in our methodology, aiming to derive dispatching rules that commute with simulation methods.

The paper is organized as follows. 
Section~\ref{sec:lit_rev} provides a literature review.
In Section~\ref{sec:problem_f}, we formulate SMSP in terms of the well-known Flexible Job Shop Scheduling Problem (FJSSP). 
% and Section \ref{sec:aco} describes the overview of the ACO approach. 
Our GSACO-O algorithm is presented in Section~\ref{sec:gsaco}.
In Section~\ref{sec:sim}, we describe a customized simulation framework extending \cite{Kovacs2022}.
Section~\ref{sec:results} provides and discusses experimental results.
Finally, Section~\ref{sec:conclusion} concludes the paper.


%The complexity of scheduling is intensified by the unpredictable nature of processing times and machine availabilities. Variability in processing times may arise from differences in equipment performance, material handling durations, or the unique characteristics of each set of wafers. Furthermore, frequent machine breakdowns can lead to substantial disruptions, underscoring the need for strong and adaptable scheduling strategies \cite{leachman1996benchmarking}.

%Scheduling in large-scale semiconductor production is a cornerstone of operational management that directly influences the effectiveness and efficiency of the entire manufacturing process \cite{schumann2022scheduling}. It involves planning and organizing production activities to ensure that resources are utilized optimally and product flows are synchronized across various stages of the manufacturing process. Effective scheduling is critical not only for maintaining high throughput but also for minimizing makespan.

%The scheduling of semiconductor manufacturing is notably complex due to the high variability in production processes, the sensitive nature of the materials involved, and the stringent quality requirements \cite{May2006}. Each semiconductor product may pass through hundreds of processing steps, requiring precise timing and coordination. Moreover, the high mix of product types, each with different processing needs and priorities, adds another layer of complexity \cite{Mönch2011}. This complexity is further exacerbated by the need to integrate new product introductions seamlessly into the production schedule without disrupting ongoing operations.

%Scheduling production operations within the intricate landscape of semiconductor manufacturing represents one of the most daunting challenges in resource allocation. The dynamic nature of manufacturing environments—characterized by unpredictable fluctuations in process and demand, supply chain delays, and frequent machine breakdowns—significantly intensifies this complexity. Consequently, production scheduling must not only strive for near-optimal outcomes but also maintain robustness and flexibility to adapt swiftly to frequent changes in the production landscape. 