% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage{helvet,times,courier}
\usepackage{multirow}
\usepackage{algorithm2e}
\SetKwInput{KwParam}{Parameters}
\SetKw{KwFrom}{from}
\SetCommentSty{textit}

\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\sloppy
\hyphenation{make-span}
\begin{document}
%
\title{Swarm Intelligence-Driven Dispatching Rules for Large-Scale Semiconductor Production: Integrating Simulation and Optimization to Enhance Operational Efficiency
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Ramsha Ali\inst{1}\orcidID{0000-0002-4794-6560} \and
Peyman Eftekhari\inst{1}\orcidID{0009-0007-4198-392X} \and
Martin Gebser\inst{1}\orcidID{0000-0002-8010-4752} \and
Stephan Leitner\inst{2}\orcidID{0000-0001-6790-4651} \and
Gerhard Friedrich\inst{1}\orcidID{0000-0002-1992-4049}
}
%
\authorrunning{R. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Department of Artificial Intelligence and Cybersecurity, \and
	Department of Management Control and Strategic Management, \\ University of Klagenfurt, Austria \\
	\email{\{ramsha.ali,peyman.eftekhari,martin.gebser, \\ stephan.leitner,gerhard.friedrich\}@aau.at} \\
	\url{https://www.aau.at}}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The escalating complexity of semiconductor production, characterized by high-volume, low-mix and low-volume, high-mix environments, demands advanced dispatching strategies that transcend traditional rule-based systems. This paper introduces a novel set of dispatching rules derived from Swarm Intelligence techniques, specifically designed to tackle the intricate dynamics of large-scale semiconductor manufacturing. The research integrates simulation and optimization methodologies to investigate and enhance operational efficiency, addressing both the scalability of solutions and their practical implementation. We employ a customizable simulation framework to model a semiconductor manufacturing environment, wherein various dispatching rules, including FIFO, CR, RANDOM, and our proposed SI-driven method, are assessed. The core of our approach lies in its ability to adaptively reconfigure scheduling priorities based on real-time production dynamics, thus significantly improving the responsiveness and throughput of manufacturing processes.
The effectiveness of these dispatching rules is quantitatively evaluated through a series of simulations that measure key performance indicators such as Work in Progress (WIP) levels, throughput, and operational variability across different production scenarios.
This study not only elucidates the potential of swarm intelligence in refining production dispatching but also provides a framework that incorporates scalable simulation tool that can assist in the further development of intelligent dispatching systems. 

\keywords{Swarm intelligence \and Ant colony optimization \and Greedy search \and Semiconductor production \and Scheduling \and Dispatching \and Simulation}
\end{abstract}
%
%
%
\section{Introduction}
\label{sec:introduction}
\input{introduction.tex}

\section{literature Review}
\label{sec:lit_rev}
\input{lit_review.tex}

\section{Problem Formulation}
\label{sec:problem_f}
\input{problem_formulation.tex}

\section{GSACO Algorithm}
\label{sec:gsaco}
\input{gsaco_algo.tex}

\section{Simulation}
\label{sec:sim}
\input{simulation.tex}

\section{\uppercase{Experimental Evaluation}}
\label{sec:results}
\input{experimental_evaluation.tex}


\section{Conclusion}
\label{sec:conclusion}

Modern semiconductor fabs are highly complex and dynamic production
environments, whose efficient operation by means of automated scheduling
and control systems constitutes a pressing research challenge.
In this work, we model the production processes of large-scale
semiconductor fabs in terms of the well-known FJSSP.
In contrast to classical FJSSP benchmarks,
this leads to large-scale scheduling problems,
even if short planning horizons cover only a fraction of the long
production routes with hundreds of operations.
The resulting size and complexity of large-scale SMSP instances
exceed the capabilities of common FJSSP solving methods.
We thus propose the GSACO algorithm combining probabilistic
operation sequencing with greedy machine assignment.
Its efficient implementation utilizing tensor operations and
parallel ant simulations enables GSACO's convergence to high-quality
solutions in short time.
In this way, GSACO overcomes the scalability limits of
exact optimization by means of a state-of-the-art CP approach
and achieves the performance required for frequent re-scheduling
in reaction to process deviations. % in physical fabs.


While simplified FJSSP models of semiconductor manufacturing processes
provide insights regarding the scalability of scheduling methods,
in future work, we aim at extending GSACO to incorporate the specific
conditions and functionalities of tools performing the production operations.
Such features include, e.g.,
machine setups to be equipped before performing operations,
preventive maintenance procedures for which a machine needs to stay idle, and
batch processing capacities to handle several production lots in one pass.
In practice, these specifics matter for machine assignment strategies
and should also be reflected in the respective greedy phase of GSACO.

Our second target of future work concerns the utilization of schedules 
found by GSACO for decision making and control within simulation models
of semiconductor fabs.
This goes along with the extension of optimization objectives to
practically relevant performance indicators, such as deadlines for the
completion of jobs and minimizing the tardiness.
In view of the dynamic nature of real-world production operations and
unpredictable stochastic events,
quantifying the improvements by optimized scheduling methods
requires their integration and evaluation in simulation.


\section*{Acknowledgments}

This work has been funded by the FFG project 894072 (SwarmIn).
We are grateful to the anonymous reviewers for constructive 
comments that helped to improve the presentation of this paper.




%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\input{bib.tex}
\end{document}
